Superabsorption of light by nanoparticles

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

When we mix the different sized spheres, there will be an effect of
their mutual interaction. To take this into account, we simulate a
dimer configurations with 0 nm, 10 nm and 30 nm separation between
spheres.  The resulting spectra have a strong contribution from
standalone resonances, while coupling effects seems to be relatively
minor. This can be explained from modal field distribution in
Fig.~4(c) of the manuscript. Positioning spheres in H-k plane we are
exploiting the features of fields being highly localized inside the
spheres. Arranging spheres in other planes with respect to incident
polarization, or increasing the number of interacting spheres can
change the effect of coupling. As an example, we tested arrangement of
spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the
interaction between spheres is strong, however, due to near-field
nature of this coupling, it rapidly decays with the separation width
Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of
individual particles dominate in overall spectra for both planes of
polarization. This way we show that in principle it is possible to
construct an absorption band of an array of dispersed particles simply
optimizing the properties of individual particles.

In order to reflect these findings in the manuscript, we have
rewritten the text from ``As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.'' to ``As a result, one can design
absorbers with broad spectra or spectrally-selective absorbers with
almost arbitrary prescribed properties.  One can also achieve
broadband performance by mixing particles whose absorption is
optimized for different wavelengths. We have verified that due to
strong localization of electric dipole field it is possible to design
dimers whose absorbing properties are dominated by the properties of
individual particles, and not by their mutual interaction. As a
result, by appropriately spacing the resonances of individual
particles, their mixture will exhibit a combined broadband
response. Providing such an additional control, this approach
complements the case of self-organized particles of various size and
shape, which was experimentally proved to have a wide absorption
band~[ACS-AMI-Liu-2015]. % Reference to the paper mentioned with the
% reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.''

@@

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2. To achieve super-absorption behavior, it is interesting
  to know what will happen when the multilayered nanoparticles are
  closely packed as the plasmonic crystal. As reported in the previous
  papers [ACS Applied Materials \& Interfaces, 7, 4962−4968 (2015);
  Materials Letters 158, 262–265 (2015); Applied Physics Letters, 104,
  081116 (2014); Nanotechnology, 24, 155203 (2013)], the packed
  plasmonic crystals have been demonstrated to show broadband light
  coupling and confinement. Thereby, it would be interesting to show
  improved broadband light absorption based on the plasmonic crystal
  of this proposed multilayered nanoparticles. 
\end{tabular}

We would like to thank the reviewer for the references. We have
included them into our manuscript with relevant discussions,
% ACS-AMI was added to reply on the previous comment, ML and NT can be added to
% the links on plasmonic devices in introduction along with [19,20].
with one exception. Reference Applied Physics Letters, 104, 081116
(2014) with the title "$\lambda^3$/20000 plasmonic nanocavities with
multispectral ultra-narrowband absorption for high-quality sensing''
is not related to broadband light coupling and confinement'' and was
probably listed by an accident.

We agree with the referee that closely packed particles can lead to
the increase of the bandwidth. This broadening originates from the
appearance of a collective mode (or, in other words, the hybridization
of plasmon responses of several particles) with additional impact from
retardation effects. While for some resonances, as we have discussed
in the response to the previous comment, the interaction between our
nanoparticles can be weak, it should still be possible to optimize
simultaneously the geometry of individual particles and the array
parameters to achieve enhanced absorption. As a proof of concept, we
performed FDTD simulations of the 3x3 square array of spheres (to
provide a good coupling both in E and H directions) with the
separation of 4~nm, see Fig~\ref{fig:fdtd-3x3}(a). Several collective
modes can be recognized from field distribution while changing the
incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). We see that for the
used materials, nanoparticle and array designs, spectral range, and
plane of polarization, we observed a broadened resonance, with the
broadening mostly occurring in the blue shift direction
Fig~\ref{fig:fdtd-3x3}(b).

@@

In the end of the first paragraph of page 3, right column, after
``..., since it should be easier and cheaper to fabricate.'' We add:
``At the same time the best absorption efficiency for larger particles
(with $R>60$~nm for provided materials) can be achieved in
superabsorption regime. This may be important when fabrication of
smaller multi-layer particles is not available.''

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2.  In Fig. 2, we noticed a discontinuity at $\sim$80
  nm. The authors explain it as the design supporting electric dipole
  and magnetic quadrupole has larger ACS. However, this explanation is
  not clearly to me since it is lacking physics behind this
  phenomenon. The authors should clarify why the magnetic quadrupole
  only plays a significant role in this small wavelength range.
\end{tabular}

The short qualitative answer to this is that it is not possible to
excite the magnetic quadrupole resonance to the particle of a smaller
size, and, it is hard to keep it efficient for larger sizes, while
also maintaining the large contribution of the electric dipole.

To present this idea in more details we run an optimization with
changed fitness function - we maximize the absorption efficiency of
only the electric dipole, with results presented in
Fig.~\ref{fig:a1max}. With the increase of the particle radius $R$ the
$\tilde{a}_1$ rapidly reaches its theoretical maximum. Optimizer was
quite successful in maintain this for all larger values of $R$. When
we increase the $R$, other multipole resonances can appear. Such an
appearance of $\tilde{b}_2$ forms the discussed maxima at $\sim
80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).

Another way to qualitatively explain the effect is the following. We
have a multiple resonance structure, and by changing parameters we can
overlap several different resonances. Depending on the total particle
size, different combination of resonances can give maximum absorption,
therefore it is not surprising that in a certain parameter range, the
combination of electric dipole and magnetic quadrupole can give us the
best possible absorption.

@@

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.  In Fig. 3 (c), the authors observed a flat top of electric
dipole resonance. They attributed this flat resonance to the excited
several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly.
\end{tabular}

We thank the referee for pointing this out, we must have not explained
this point clearly. The most interesting feature of this resonance
that we wanted to bring attention to is that the resonance has an
unusual flat top part. The main shape and width of the resonance is
explained by one dominating dipole mode, as it is seen in the mode
decomposition in Fig.~3(d). Two additional electric dipole resonances
are much weaker, but their contribution "flattens" the top of the
combined absorption resonance. We have clarified this in the modified
manuscript changing the caption of Fig.~(3), after ``Panel~(d) shows
the superposition of the squared absolute values of the Mie
coefficients for electric dipole contribution inside each layer'' we
added ``of design from panel~(c), which is needed to explain an almost
flat top of the electric dipole resonance.''

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.  Some sentences are not clear to me. For instance, “there
is a strong conterplay between the increased absorption for larger
particles vs size for smaller particles”.  In summary, I do not think
the manuscript is acceptable at its current stage.
\end{tabular}%

We have worked on improving the readability of the
manuscript. Particularly, we changed the instance mentioned with the
reviewer, full sentence in the updated manuscript is now the
following: ``Here we show that the increased peak absorption rate of
high order multipoles available in larger particles does not
compensate the increased volume with low absorption rate compared to
volume of smaller particles, and quite remarkably we find that the
most {\em efficient} absorption can be achieved in a single channel
limit for small particles.''

### 2015-09-27 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Moved changed from the response letter to the manuscript

Mie theory,\cite{Mie-1908} which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these
days,\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011}
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to the study of multilayer spherical
particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
various applications in cancer treatment,\cite{Zhang-2010,
  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices,\cite{Martin-2013, Alu-2005} in the study of
thermal properties of insulating materials,\cite{Xie-2013} as well as
for improving solar cells performance.\cite{Kameya-2011,Mann-2011}

@@

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles. Here we
show that there is a strong counterplay between the increased
absorption for larger particles vs size for smaller particles, and
quite remarkably we find that the most {\em efficient} absorption can
be achieved in a single channel limit for small particles.

@@

Remarkably, the absolute maximum {\em absorption efficiency} is not
reached within the superabsorption regime. Figure~\ref{fig:overview}
shows that the maximum efficiency is achieved for small particle size,
and the ACS is still well below the single channel limit. It appears
that the $Ag/Si$ core-shell nanoparticle with the total radii of
approximately 36~nm is the most efficient absorber among the
considered structures, whose ACS reaches values {\em over 5 times the
  physical cross-section area of the particle}.  From a practical
point of view, it is quite important that the maximum can be reached
in a bi-layer structure, instead of a triple-layer, since it should be
easier and cheaper to fabricate.

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

@@

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design spectrally-selective
absorbers or broadband absorbers with almost arbitrary prescribed
properties. We note, that using this algorithm, one can optimize not
only absorbtion efficiency, but also other parameters that may be
desired for some applications. As an example we reproduce some of the
results from the work of Estakhri and Al\`u,\cite{Alu-2014} where
authors aim to design absorbers with small scattering cross-section,
and we provide a number of new optimized designs. The efficiency in
the Ref.\cite{Alu-2014} is defined as the ACS normalized to
scattering cross-section. Initially, we set the total value of the
absorbed power with cross-section of $\alpha_{\rm
  abs}=\frac{3\lambda^2}{8\pi}$ and keep the outer radius of the
particle fixed. In this case the optimization gives a result similar
to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
Ref.\cite{Alu-2014}  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
-10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
obtained radii $\{a_{c1},a_{c2},a_3\}=\{0.142,0.166,0.194\}\lambda$
and scattering-normalized absorption efficiency $\eta_{\rm
  abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
  abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
However, if we set the optimizer to keep high level of absoption
efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
and the size of the outer layer vanishes
$\{a_{c1},a_{c2}\}=\{0.00635,0.00747\}\lambda$ resulting in $\eta_{\rm
  abs}^{(Q)} =544$.  It means that this small particle still absorbs
five times its phisical size with a very large scattering-normalized
absorption efficiency.

>>>>

Mie theory,\cite{Mie-1908} which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these
days,\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011}
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to the study of multilayer spherical
particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
various applications in cancer treatment,\cite{Zhang-2010,
  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005, Liu-Nanotech-2013} in the study of
thermal properties of insulating materials,\cite{Xie-2013} as well as
for improving solar cells performance.\cite{Kameya-2011,Mann-2011}

@@

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles.  Here we
show that the increased peak absorption rate of high order multipoles
available in larger particles does not compensate the increased volume
with low absorption rate compared to volume of smaller particles, and
quite remarkably we find that the most {\em efficient} absorption can
be achieved in a single channel limit for small particles.

@@

Remarkably, the absolute maximum {\em absorption efficiency} is not
reached within the superabsorption regime. Figure~\ref{fig:overview}
shows that the maximum efficiency is achieved for small particle size,
and the ACS is still well below the single channel limit. It appears
that the $Ag/Si$ core-shell nanoparticle with the total radii of
approximately 36~nm is the most efficient absorber among the
considered structures, whose ACS reaches values {\em over 5 times the
  physical cross-section area of the particle}.  From a practical
point of view, it is quite important that the maximum can be reached
in a bi-layer structure, instead of a triple-layer, since it should be
easier and cheaper to fabricate.  At the same time the best absorption
efficiency for larger particles (with $R>60$~nm for provided
materials) can be achieved in superabsorption regime. This may be
important when fabrication of smaller multi-layer particles is not
available.

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer
      of design from panel~(c), which is needed to explain an almost
      flat top of the electric dipole resonance.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

@@

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proved
to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

We note, that using this algorithm, one can optimize not
only absorbtion efficiency, but also other parameters that may be
desired for some applications. As an example we reproduce some of the
results from the work of Estakhri and Al\`u,\cite{Alu-2014} where
authors aim to design absorbers with small scattering cross-section,
and we provide a number of new optimized designs. The efficiency in
the Ref.\cite{Alu-2014} is defined as the ACS normalized to
scattering cross-section. Initially, we set the total value of the
absorbed power with cross-section of $\alpha_{\rm
  abs}=\frac{3\lambda^2}{8\pi}$ and keep the outer radius of the
particle fixed. In this case the optimization gives a result similar
to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
Ref.\cite{Alu-2014}  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
-10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
obtained radii $\{a_{c1},a_{c2},a_3\}=\{0.142,0.166,0.194\}\lambda$
and scattering-normalized absorption efficiency $\eta_{\rm
  abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
  abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
However, if we set the optimizer to keep high level of absoption
efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
and the size of the outer layer vanishes
$\{a_{c1},a_{c2}\}=\{0.00635,0.00747\}\lambda$ resulting in $\eta_{\rm
  abs}^{(Q)} =544$.  It means that this small particle still absorbs
five times its phisical size with a very large scattering-normalized
absorption efficiency.
